Centralized Programming for Distributed Control Planes

### 2016-01-28 paper/evaluation.tex
Adding description to evaluation.

\section{Evaluation}

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
For the data center policy, we measure the mean compilation time per-prefix since the \sysname compiler can compile for each prefix independently, and in parallel. Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase. No individual compilation phase dominates the running time of the compiler, with construction and minimization of the product graph taking the most time. \sysname compiles each data center in under 15 seconds per-prefix on average. Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
\todo{Core compilation times here}

\ryan{Do we want to include this?}
The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center policy. Minimization significantly reduces the size of the naive configurations.

>>>>

\section{Evaluation}
\label{sec:evaluation}

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
For the data center policy, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel. Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase. No individual compilation phase dominates the running time of the compiler, with construction and minimization of the product graph taking the most time. \sysname compiles each data center in under 15 seconds per-prefix on average. Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
%
For the backbone policy, the \sysname compiler scales hundreds of routers, in a little over a minute per-prefix. However, unlike the data center policy, the number of prefixes for the backbone policy stays relatively fixed. Total compilation time for the largest backbone topology tested, with 200 routers, takes less than 3 minutes total. The presence of more preferences in the backbone policy increases the size of the product graph, and means minimization becomes a more expensive step in compilation.

The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center and backbone policies. In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.
